### 2021-06-29 rad-icfp-2021/generalisation.tex
writing optim table

\MH{I think I only present two: conditionals, and general case for array. partial op can be dealt with before. HO function mentioned at the end}

Extended source language:

\input{figures/generalisation_source_grammar}

@@

@@

\subsection{Higher-order functions}

>>>>

% Extended source language:

% \input{figures/generalisation_source_grammar}

@@

\subsubsection{Lifting the restriction on map and fold}
\label{ssub:Lifting the restriction on map and fold}

\subsubsection{Lifting the restriction on the type of arrays}
\label{ssub:Lifting the restriction on the type of arrays}

@@
